### 2012-06-21 inst/examples/cautious.Rmd
Example of cautious (non-optimal) strategy, fishing at fixed fraction of optinal

`ro tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache=TRUE, cache.path="May/" or`

@@

``` {r }
f <- May
````

@@

``` {r }
pars <- c(r = .75, k = 10, a=1, H=1, Q = 3)
K <- 8 # approx
````

@@

``` {r }
xmin <- 0
xmax <- 1.5 * K
grid_n <- 100
````

@@

``` {r  grid}
x_grid <- seq(xmin, xmax, length = grid_n)  
h_grid <- x_grid  
````

``` {r miscpars}
delta <- 0.05
xT <- 0
OptTime <- 200
sigma_g <- .5
````

@@

``` {r  SDP_Mat}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g)
````

@@

Bellman's algorithm to compute the optimal solution for all possible trajectories.

``` {r  find_dp_opt }
opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=OptTime, xT=xT, 
                     profit, delta=delta, reward=0)
````

@@

``` {r policyfn_plot}
q1 <- qplot(x_grid, x_grid - x_grid[opt$D[,1]], xlab="stock size", ylab="escapement") + 
geom_point(aes(x,y), data=data.frame(x=opt$S, y=opt$S), col="red")
q1
````

@@

``` {r valuefn_plot}
q2 <- qplot(x_grid, opt$V, xlab="stock size", ylab="value") + 
geom_vline(xintercept=opt$S)
q2
````

@@

Now we'll simulate 100 replicates of this stochastic process,
``` {r  simulate }
sims <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i)
})
````

@@

``` {r  p1}
p1 <- ggplot(dt) + geom_abline(intercept=opt$S, slope = 0) + 
  geom_abline(intercept=xT, slope = 0, lty=2) 
p1 <- p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.2)
p1
````

>>>>

`ro tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache=TRUE, cache.path="cautious/" or`

@@

``` {r stateeqn}
f <- May
````

@@

``` {r pars}
pars <- c(r = .75, k = 10, a=1, H=1, Q = 3)
K <- 8 # approx
````

@@

``` {r gridpars}
xmin <- 0
xmax <- 1.5 * K
grid_n <- 100
````

@@

``` {r  grid, dependson="gridpars"}
x_grid <- seq(xmin, xmax, length = grid_n)  
h_grid <- x_grid  
````

``` {r miscpars}
delta <- 0.05
xT <- 0
OptTime <- 25
sigma_g <- .5
````

@@

``` {r  SDP_Mat, dependson="grid"}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g)
````

@@

Bellman's algorithm to compute the a cautious solution that selects a fraction `P` = `r P <- 1` of the optimal harvest solution for all possible trajectories in the iterative optimization.

``` {r  find_dp_opt, dependson="SDP_Mat"}
opt <- find_dp_cautious(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                     profit, delta, reward=0, P = P)
````

@@

``` {r policyfn_plot, dependson="find_dp_opt"}
q1 <- qplot(x_grid, x_grid - x_grid[opt$D[,1]], xlab="stock size", ylab="escapement") + 
geom_point(aes(x,y), data=data.frame(x=opt$S, y=opt$S), col="red")
q1
````

@@

``` {r valuefn_plot, dependson="find_dp_opt"}
q2 <- qplot(x_grid, opt$V, xlab="stock size", ylab="value") + 
geom_vline(xintercept=opt$S)
q2
````

@@

Now we'll simulate 100 replicates of this stochastic process,
``` {r  simulate, dependson="find_dp_opt" }
sims <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i)
})
````

@@

``` {r  p1, dependson="tidy"}
p1 <- ggplot(dt) + geom_abline(intercept=opt$S, slope = 0) + 
  geom_abline(intercept=xT, slope = 0, lty=2) 
p1 <- p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.2)
p1
````
``` {r  p2, dependson="tidy"}
p2 <- ggplot(dt) + geom_abline(intercept=opt$S, slope = 0) + 
  geom_abline(intercept=xT, slope = 0, lty=2) 
p2 <- p2 + geom_line(aes(time, harvest, group = reps), alpha = 0.2)
p2
````

``` {r profits, fig.cap="the distribution of profits by scenario", dependson="tidy"}
profits <-dt[ , sum(profit), by="reps"] 
ggplot(profits) + geom_histogram(aes(V1)) 
````
